---
output: 
html_fragmen:
citation_package: natbib
keep_tex: false
fig_caption: true
latex_engine: pdflatex
title: Short-term forecasts of COVID-19 deaths in multiple countries
author:
- name: Sangeeta Bhatia
affiliation: Imperial College London
abstract: 
keywords: 
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 11pt
spacing: double
bibliography: 
biblio-style: apsr
endnote: no
---

```{r echo = FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(
    echo = FALSE, 
    fig.width = 21, 
    fig.height = 15,
    warning = FALSE,
    messages = FALSE
)

```

```{r}
week_ending <- as.Date(week_ending)
ens_rt_both <- readr::read_rds("ensemble_model_rt.rds")
ens_rt <- ens_rt_both[ens_rt_both$si == "si_2", ]
ens_rt$model <- as.Date(ens_rt$model)
ens_rt <- ens_rt[ens_rt$model == max(ens_rt$model), ]
x <- tidyr::spread(ens_rt, quantile, out2)
x$country <- snakecase::to_title_case(x$country)
stable <- x[x$`2.5%` < 1 & x$`97.5%` > 1, ]
declining <- x[x$`97.5%` < 1, ]
growing_slow <- x[x$`2.5%` > 1 & x$`97.5%` < 2, ]
growing_fast <- x[x$`2.5%` > 1 & x$`97.5%` > 2, ]

#### Deaths
ensemble_weekly_qntls <- readr::read_rds("ensemble_weekly_qntls.rds")
ensemble_weekly_qntls$country <- snakecase::to_title_case(ensemble_weekly_qntls$country)
ensemble_weekly_qntls_si1 <- ensemble_weekly_qntls[ensemble_weekly_qntls$si == "si_2", ]
ensemble_weekly_qntls_si1 <- ensemble_weekly_qntls_si1[ensemble_weekly_qntls_si1$proj == week_ending, ]
small <- ensemble_weekly_qntls_si1[ensemble_weekly_qntls_si1$`50%` < 100, ]
rel_large <- ensemble_weekly_qntls_si1[ensemble_weekly_qntls_si1$`50%` > 100 &
                                       ensemble_weekly_qntls_si1$`50%` < 1000, ]
large <- ensemble_weekly_qntls_si1[ensemble_weekly_qntls_si1$`50%` > 1000 &
                                   ensemble_weekly_qntls_si1$`50%` < 5000, ]

very_large <- ensemble_weekly_qntls_si1[ensemble_weekly_qntls_si1$`50%` > 5000, ]

                                       
```


*Forecasts and Transmissibility Estimates*

Based on our best estimates of transmissibility, the COVID-19 epidemic
is:

-   likely declining^1^ in `r nrow(declining)`	 countries <br/> 
(`r declining$country`);
-	likely stabilising^2^  in `r nrow(stable)` countries <br/>
(`r stable$country`);
-	likely growing slowly^3^ in `r nrow(growing_slow)` countries <br/>
(`r growing_slow$country`);
-	likely growing rapidly^4^ in `r nrow(growing_fast)` countries <br/>
(`r growing_fast$country`).

Based on the central trends in the forecasts, the total number of
reported deaths in the coming week is expected to be:

-	relatively small in `r nrow(small)` countries (<100 deaths) <br/>
(`r small$country`);
-	relatively large in `r nrow(rel_large)` countries (100 to 1000 deaths) <br/>
(`r rel_large$country`),
-	large in `r nrow(large)` countries (1,000 to 5,000 deaths) <br/>
(`r large$country`),
-	very large in `r nrow(very_large)` countries (> 5,000 deaths) <br/>
(`r very_large$country`).



<br>
<br>
<br>
<br>

1. if the 97.5^th^ percentile of $R_t$ is below 1.
2. if the 95% Credible Interval (CrI) of $R_t$ contains 1.
3. if the 2.5^th^ percentile of $R_t$ is greater than 1 and the
97.5^th^ percentile is less than 2. 
4. if the 97.5^th^ percentile of $R_t$ is greater than 2.
