---
output: 
pdf_document:
citation_package: natbib
keep_tex: false
fig_caption: true
latex_engine: pdflatex
title: 
author:
- name: Sangeeta Bhatia
affiliation: Imperial College London
abstract: 
keywords: 
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 11pt
spacing: double
bibliography: 
biblio-style: apsr
endnote: no
---

```{r setup, eval = TRUE}
library(dplyr)
library(purrr)
library(ggplot2)
```
## Proportion in Credible Interval

```{r}
unwtd_pred_error <- readr::read_csv("unwtd_pred_weekly_summary.csv")
x <- mean(unwtd_pred_error$prop_in_50_mu)
x_sd <- sd(unwtd_pred_error$prop_in_50_mu)

y <- mean(unwtd_pred_error$prop_in_975_mu)
y_sd <- sd(unwtd_pred_error$prop_in_975_mu)

mae <- mean(unwtd_pred_error$rel_mae_mu)
mae_sd <- sd(unwtd_pred_error$rel_mae_mu)

```

- Overall the proportion of observations in 50% CrI is
`r scales::percent(x, 0.1)`, SD: `r scales::percent(x_sd, 0.1)` .

- Overall the proportion of observations in 95% CrI is
`r scales::percent(y, 0.1)`, SD: `r scales::percent(y_sd, 0.1)`.

- Mean relative error across all countries and all weeks of 
forecasts was `r signif(mae, 3)`. SD of relative
mean error was `r signif(mae_sd, 3)`.


```{r}

better_than_null <- readRDS("better_than_null.rds")
better_than_linear <- readRDS("better_than_linear.rds")

x <- sum(better_than_null$n_less_than_1) / sum(better_than_null$n_forecasts)
y <- sum(better_than_linear$n_less_than_1) / sum(better_than_linear$n_forecasts)
```

- The relative error of the model was smaller than the error a null 
model would have made in `r scales::percent(x, 0.1)` of weeks for which forecasts were
produced.

- The relative error of the model was smaller than the error a null 
model would have made in `r scales::percent(y, 0.1)` of weeks for which forecasts were
produced.
