---
title: "ccc"
author: "Pierre Nouvellet"
date: "2019-07"
---

```{r options, include = FALSE, message = FALSE, warning = FALSE, error = FALSE}
set.seed(1)
# runif(1,0,1)
library(knitr)
library(EpiEstim)
library(Hmisc)

opts_chunk$set(collapse = TRUE)

opts_chunk$set(fig.path='figs/', fig.keep='high', 
               dev=c('png'), fig.width=8, fig.height=8, cache=FALSE,
               tidy=FALSE, warning=FALSE, fig.show="asis"
 	       )

# useful functions
sapply(paste0('Rscript/MCMC/',(list.files('Rscript/MCMC/'))),FUN = source)


```


NEED to do:
1) input

# Input

```{r}

date_week_finishing <-  as.Date('31/05/2020',format = '%d/%m/%Y')

day.project <- 7
t.window.range <- 10

rep <- 5e4

```

# Read data

```{r,fig.height=8,fig.width=5}
d <- readRDS(file = paste0('../Rdata/data_',date_week_finishing,'.rds'))

I <- d$D_active_transmission
country <- d$Country
N_geo <- length(country)
# date_week_finishing <- d$date_week_finishing

# plot(I$dates,I$United_States_of_America,
#      xlim=as.Date(c('16-03-20','10-06-20'),format = '%d-%m-%y'),
#      ylim = c(0,5000),bty='n',xlab = '',ylab = 'deaths',
#      xaxt="n")
# axis(side = 1, 
#      at = as.Date(c('16-03-20','10-06-20'),
#                   format = '%d-%m-%y'), 
#      labels = c('16-March','10-June'))
# library(zoo)
# ri <- rollmean(x = I$United_States_of_America, k = 7)
# lines(I$dates,c(I$United_States_of_America[1:6],ri),col='blue')
# abline(h=2000,lty = 2)
# abline(h=1000,lty = 2)
# abline(h=3000,lty = 2)
```


```{r}

## SI
### 1. Estimating R_t with EpiEstim
si_mean <- d$si_mean[2]
si_std <- d$si_std[2]
# CV_SI <- si_std / si_mean
SItrunc <- 20

## # serial interval estimate used: mean = 3.96, sd =  4.75
## # from Du et al. from The University of Texas at Austin and University of Hong Kong
## # (https://www.medrxiv.org/content/10.1101/2020.01.28.20019299v4.full.pdf)
## # (https://www.medrxiv.org/content/10.1101/2020.02.19.20025452v2.full.pdf)
SI <- SI_gamma_dist_EpiEstim(mu = si_mean,
                             si_std  = si_std,
                            SItrunc = SItrunc)

plot(seq(0, 20), SI$dist, type = "h",
          lwd = 10, lend = 1, xlab = "time (days)", ylab = "frequency")
title(main = "Discrete distribution of the serial interval of COVID-19")
```



```{r}

t.proj.start <- date_week_finishing + 1

t.window <- seq(t.proj.start-t.window.range,t.proj.start-1,1)

incidence_inference <- I[which(I$dates %in% t.window),]


```

# evaluate Rt

```{r MCMC1, eval=TRUE, echo=TRUE}

                          
sigma_prop <- rep(0.1,N_geo*2)         # initial proposal variances (they are now tuned!)
# initial incidence conditions 
if ( N_geo>1 ){
  mu0 <- as.numeric(log(colMeans(incidence_inference[,-1])*si_mean))
}else{
  mu0 <- as.numeric(log(mean(incidence_inference[,-1])*si_mean))
}
# initially, we assume R=1 and choose initial condition accordingly, i.e. with mu0 case and R=1 
# we expect the number of daily cases to stabilised at the mean of the observed incidence in the 
# time window of interest
# this is use for the prior of initial number of cases, i.e. as the mean of an exponential distribution
# in practice, the mu0 cases will happen 100 days before the start of the time windows

theta0 <- c(rep(1,N_geo), mu0)          # initial parameter R=1 (time # of locations, and initial number of cases in the past)  


source('Rscript/wrapper.v2.r')

```


### Project forward

Once we have inferred the reproduction numbers in the time window, and the initial conditions, we can use the same model to project forward.

We start the projection from the begining of the time window, to reflect incertainty in the initial conditions.

If the time window was 4 weeks, and we want to project for 4 weeks after that, then the 'week_forward' needs to be 4+4 in the function 'Sim_Poiss'.

```{r forward1, eval=TRUE , echo= TRUE}
# save.image(file = 'int_23MArch.RData')
# load(file = 'int_23MArch.RData')
NR_samples <- nrow(res$theta)/10 
Nsim_per_samples <-  10

day_forward <- day.project + t.window.range

source('Rscript/wrapper.proj.v2.r')


```


```{r}
results <- list(date_week_finishing =d$date_week_finishing,
                                  Threshold_criterion_4weeks = d$Threshold_criterion_4weeks,
                                  Threshold_criterion_7days = d$Threshold_criterion_7days,
                                  I_active_transmission = d$I_active_transmission,
                                  Country = d$Country,
                                  res_MCMC = res,
                                  I_pred = I_pred,
                                  t.proj.start = t.proj.start,
                                  t.window.range = t.window.range,
                                  day.project = day.project,
                                  SI = SI)

```


Standard output for project


```{r}
N_geo <- length(results$Country)

Rt_last <- data.frame(results$res_MCMC$theta[,1:N_geo])
names(Rt_last) <- results$Country
if (nrow(Rt_last)>1e4){
  f <- round(seq(1,nrow(Rt_last),length.out = 1e4))
  Rt_last <- Rt_last[f,]
}


Predictions <- list()
for (i in 1:N_geo){
  temp <- results$I_pred[[i]]
  temp <- as.data.frame(temp[,8:14])
  names(temp) <- as.character(seq(results$t.proj.start,results$t.proj.start+7-1,1))
  if (nrow(temp)>1e4){
    f <- round(seq(1,nrow(temp),length.out = 1e4))
    temp <- temp[f,]
  }
  Predictions[[as.character(results$Country[i])]] <- temp
}

Std_results <- list(I_active_transmission = d$I_active_transmission,
                    D_active_transmission = d$D_active_transmission,
                    Country = results$Country,
                    Rt_last = Rt_last,
                    Predictions = Predictions)


saveRDS(object = Std_results,
        file = paste0('RData/RtI0_Std_results_week_end_',date_week_finishing,'.SI2.rds' ))
```

