---
output: 
html_fragment:
citation_package: natbib
keep_tex: false
fig_caption: true
latex_engine: pdflatex
title: Short-term forecasts of COVID-19 deaths in multiple countries
author:
- name: Sangeeta Bhatia
affiliation: Imperial College London
abstract: 
keywords: 
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 11pt
spacing: double
bibliography: 
biblio-style: apsr
endnote: no
---

```{r setup, eval = TRUE}

knitr::opts_chunk$set(
    echo = FALSE, 
    fig.width = 21, 
    fig.height = 15,
    warning = FALSE,
    messages = FALSE
)
```


### Key results on transmissibility and forecasting


```{r}

ens_rt_both <- readr::read_rds("ensemble_model_rt.rds")
ens_rt <- ens_rt_both[ens_rt_both$si == "si_2", ]
ens_rt$model <- as.Date(ens_rt$model)
ens_rt <- ens_rt[ens_rt$model == max(ens_rt$model), ]
date_week_finishing <- max(ens_rt$model)
ens_rt_tall <- tidyr::spread(ens_rt, quantile, out2)
ens_rt_tall$country <- snakecase::to_title_case(ens_rt_tall$country)
top2_rt <- dplyr::top_n(ens_rt_tall, n = 2, wt = `50%`) %>%
    dplyr::mutate_if(is.numeric, ~ format(round(., 2), nsmall = 1))
bottom2_rt <- dplyr::top_n(ens_rt_tall, n = -2, wt = `50%`) %>%
        dplyr::mutate_if(is.numeric, ~ format(round(., 2), nsmall = 1))


ensemble_weekly_qntls <- readr::read_rds("ensemble_weekly_qntls.rds")
ensemble_weekly_qntls_si1 <- ensemble_weekly_qntls[ensemble_weekly_qntls$si == "si_2", ]
ensemble_weekly_qntls_si1 <- ensemble_weekly_qntls_si1[ensemble_weekly_qntls_si1$proj == date_week_finishing, ]
top2_deaths <- dplyr::top_n(x = ensemble_weekly_qntls_si1, n = 2, wt = `50%`) %>%
    dplyr::mutate_if(is.numeric, ~signif(., 3)) %>%
    dplyr::mutate_if(is.numeric, ~prettyNum(., big.mark = ",")) %>%
    dplyr::mutate_at(vars("country"), ~ snakecase::to_any_case(., case = "title"))

bottom2_deaths <- dplyr::top_n(x = ensemble_weekly_qntls_si1, n = -2, wt = `50%`) %>%
    dplyr::mutate_if(is.numeric, ~signif(., 3)) %>%
    dplyr::mutate_if(is.numeric, ~prettyNum(., big.mark = ",")) %>%
    dplyr::mutate_at(vars("country"), ~ snakecase::to_any_case(., case = "title"))

```
Key results below are based on an ensemble forecast of two models.

Transmissibility is characterised by the reproduction number R~t~, i.e., the 
average number of cases that one infected individual is likely to
infect. Analysis of transmissibility indicates that the reproduction 
numbers last week (week starting 
`r format(as.Date(date_week_finishing, format = "%d-%m-%Y"), format = "%d-%m-%Y")`) were highest in:
  
* `r top2_rt$country[1]` with an estimated median R~t~ of 
`r top2_rt[["50%"]][1]` (95% CrI - `r top2_rt[["2.5%"]][1]` - `r top2_rt[["97.5%"]][1]`), and
* `r top2_rt$country[2]` with an estimated median R~t~ of 
`r top2_rt[["50%"]][2]` (95% CrI `r top2_rt[["2.5%"]][2]` - `r top2_rt[["97.5%"]][2]`).

and were lowest in:
  
* `r bottom2_rt$country[1]` with an estimated median R~t~ of 
`r bottom2_rt[["50%"]][1]` (95% CrI `r bottom2_rt[["2.5%"]][1]` - `r bottom2_rt[["97.5%"]][1]`), and
* `r bottom2_rt$country[2]` with an estimated median R~t~ of 
`r bottom2_rt[["50%"]][2]` (95% CrI `r bottom2_rt[["2.5%"]][2]` - `r bottom2_rt[["97.5%"]][2]`).

Forecasts of predicted deaths in the coming week (week starting `r format(as.Date(date_week_finishing, format = "%d-%m-%Y"), format = "%d-%m-%Y")`) are highest in:
  
* `r top2_deaths$country[1]` with an estimated median
`r top2_deaths[["50%"]][1]` deaths 
 (95% CrI `r top2_deaths[["2.5%"]][1]` - 
 `r top2_deaths[["97.5%"]][1]`), and
* the `r top2_deaths$country[2]` with an estimated median 
`r top2_deaths[["50%"]][2]` deaths
(95% CrI `r top2_deaths[["2.5%"]][2]` - `r top2_deaths[["97.5%"]][2]`).

and are lowest in:
  
* `r bottom2_deaths$country[1]` with an estimated median
`r bottom2_deaths[["50%"]][1]` deaths (95% CrI `r bottom2_deaths[["2.5%"]][1]` - `r bottom2_deaths[["97.5%"]][1]`), and
* `r bottom2_deaths$country[2]` with an estimated median 
`r bottom2_deaths[["50%"]][2]` deaths (95% CrI `r bottom2_deaths[["2.5%"]][2]` - `r bottom2_deaths[["97.5%"]][2]`).
