---
title: "Short and medium term forecasts for COVID-19"
runtime: shiny
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    theme: simplex

---




```{r setup, include=FALSE}

library(shiny)
library(ggthemes)
library(viridis)
library(plotly)
ensb_qntls <- readRDS("unweighted_qntls.rds")
ensb_qntls <- ensb_qntls[ensb_qntls$si == "si_2", ]
obs <- readRDS("model_input.rds")
countries <- unique(ensb_qntls$country)
forecast_weeks <- seq(
  as.Date("2020-03-08"), to = as.Date("2020-09-06"), by = "7 days"
)
long_forecasts <- readRDS("unwtd_long_qntls.rds")

country_long_pred <- reactive({
  
  pred <- long_forecasts[long_forecasts$country == input$country &
                         long_forecasts$forecast_week == input$forecast_week, ]
  pred$date <- as.Date(pred$date)
  pred
})

country_pred <- reactive({
  
  pred <- ensb_qntls[ensb_qntls$country == input$country &
                     ensb_qntls$proj == input$forecast_week, ]
  pred$date <- as.Date(pred$date)
  pred
})

country_obs <- reactive({
  
  out <- obs[, c("dates", input$country)]
  out$deaths <- out[[input$country]]
  out$dates <- as.Date(out$dates)
  out
})

```

Sidebar {.sidebar}
======================================================================

```{r}

# Define inputs
selectInput(
  'country', label = 'Select a country',
  choices = countries, selected = "Brazil"
)

selectInput('forecast_week', label = 'Select a week', choices = forecast_weeks, selected = "2020-03-08")


```

Use the __Explore metros__ tab to explore neighborhood diversity for
your chosen metropolitan area in 2010.  The red line on the
scatterplot represents a locally-weighted estimate of how diversity
varies in the metropolitan area by distance from its urban core or
cores.  Click and drag on the scatterplot to highlight the
corresponding Census tracts on the map below, and click on a Census
tract on the map to generate a chart of race and ethnicity counts.


Click the __Compare over time__ tab to examine how locally-weighted
estimates of neighborhood diversity by distance from the urban core
has varied between the 1990, 2000, and 2010 Censuses, and view maps of
these shifts over time. To learn more about the project, click the
__About__ tab.  

Short-term forecasts
======================================================================

Row
-----------------------------------------------------------------------

### Ensemble Model

```{r}
output$scatter <- renderPlotly({
  
  key <- country_pred()$country # This will uniquely identify tracts for Plotly
  pred <- country_pred()
  obs_country <- country_obs()
  p1a <- ggplot() +
    geom_point(data = obs_country, aes(dates, deaths)) +
    geom_line(data = pred, aes(date, `50%`)) +
    geom_ribbon(
      data = pred,
      aes(x = date, ymin = `2.5%`, ymax = `97.5%`),
      alpha = 0.3
    ) +
    scale_x_date(
      date_breaks = "2 weeks",
      limits = c(as.Date("2020-03-01"), NA)
    ) +
    xlab("") +
    ylab("Daily Deaths") +
    theme_minimal(base_size = 14) +
    theme(
      axis.text.x =
        element_text(angle = 90, hjust = 0.5, vjust = 0)
    )
    
  g <- ggplotly(p1a, source = 'source') %>% 
    layout(dragmode = 'lasso', 
           margin = list(l = 100), 
           font = list(family = 'Open Sans', size = 16))
  
  build <- plotly_build(g)
  
  build
    
})  
plotlyOutput('scatter', width = "80%")
```

Row 
-----------------------------------------------------------------------

### Individual Models

```{r}


```

### Reproduction Number Estimates

```{r}

```

Long-term forecasts
============================================================================

Row
----------------------------------------------------------------------------

### Forecasts

```{r}

output$long <- renderPlotly({
  
  pred <- country_long_pred()
  obs_country <- country_obs()
  p1b <- ggplot() +
    geom_point(data = obs_country, aes(dates, deaths)) +
    geom_line(data = pred, aes(date, `50%`)) +
    geom_ribbon(
      data = pred,
      aes(x = date, ymin = `2.5%`, ymax = `97.5%`),
      alpha = 0.3
    ) +
    scale_x_date(
      date_breaks = "2 weeks",
      limits = c(as.Date("2020-03-01"), NA)
    ) +
    xlab("") +
    ylab("Daily Deaths") +
    theme_minimal(base_size = 14) +
    theme(
      axis.text.x =
        element_text(angle = 90, hjust = 0.5, vjust = 0)
    )
    
  g <- ggplotly(p1b, source = 'source') %>% 
    layout(dragmode = 'lasso', 
           margin = list(l = 100), 
           font = list(family = 'Open Sans', size = 16))
  
  build <- plotly_build(g)
  
  build
    
})  
plotlyOutput('long', width = "80%")


```

Row
-----------------------------------------------------------------------------

### Reproduction Number Estimates

```{r}



```


Model performance
============================================================================




<style>

.section.sidebar {

  background-color: white; 
  font-family: "Open-Sans", "Helvetica Neue", Helvetica, Arial, sans-serif;

}

.js-irs-0 .irs-bar {
border-top-color: #1B065E;
border-bottom-color: #1B065E;
} 

.js-irs-0 .irs-bar-edge {
border-color: #1B065E;
}

.js-irs-0 .irs-single, .js-irs-0 .irs-bar-edge, .js-irs-0 .irs-bar {
background: #443A83;
}

.navbar-inverse {
background-color: #1B065E;
border-color: #1B065E;
}

.navbar-inverse .navbar-brand {
color: #1B065E;
}

a:hover, a:focus {
color: #440154;
text-decoration: underline;
}

a {
color: #443A83;
text-decoration: none;
}

.navbar-inverse .navbar-nav>li>a {
color: #a3a9ac;
}

</style>




